Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-22 JASA-template.tex
Updates.

In these simulations, our method tends
to underestimate the causal effect.
%%% MT to TB: why is the problem with a? can you explain a bit more?
This suggests that
we may want to have a different value of $a$ for these sets of observations
%%% MT to TB: is the problem that it is "fixed"? this seems a bit misleading
instead of a fixed value of $a=10$ for all of our analyses.
We can also see that the lower bound tends to improve
with increasing number of observations which validates the assumption that as we accumulate
more information, the interval becomes smaller and converges towards
the true value.

@@

For the variable identification, we use the notion of
different losses as described earlier. We consider
$\ell_1=\ell_2 = 1$ and $\ell_3= 0.2$. This is a
simplified way of choosing the loss function, we can choose more 
sophisticated loss functions based on \cite{ZAFFALON20121282}. We use this associated loss
to obtain the total loss, which we present in \cref{tab:misspec}.
In the table we denote the misspecification by counting the number of
false positives (FP) and false negatives (FN). For RBCE, we have an
additional column `ID' which denotes the number of variables which remain as
indeterminate.
From the table it can be seen that for the first scenario, our method
abstains from identifying some variables for 
$n <50$. Especially for $n=25$, our method identifies 26 and 23 variables as indeterminate
for the first setting and second setting respectively. However,
later on our method gives more precise results in terms of variable
selection. We also notice that BSSL tends to perform poorly
in terms of variable selection for $n=25$, this can be seen
from the treatment effect estimation as well.
Moreover, we observe that for the second setting both SSCE
and BSSCE underperform in identifying the active variables, which can 
be explained from \cref{tab:causal} as well.

>>>>

In these simulations, our method tends
to underestimate the causal effect.
%%% MT to TB: why is the problem with a? can you explain a bit more?
This suggests that
we may want to have a different value of $a$ for these sets of observations
%%% MT to TB: is the problem that it is "fixed"? this seems a bit misleading
instead of a fixed value of $a=10$ for all of our analyses.
We can also see that the lower bound tends to improve
with increasing number of observations: as we accumulate
more information, the interval becomes smaller and converges towards
the true value.

@@

%%% MT to TB: I changed "identification" to "selection" (assuming that is meant?)
For variable selection, we use a loss function as described earlier.
Here, we consider
$\ell_1=\ell_2=1$ and $\ell_3= 0.2$,
%%% MT to TB: I've briefly recap what these losses mean; please check if correct
i.e. we associate a loss of $1$ with false positive and false negative selections,
and a loss of $0.2$ with indeterminate selections.
Note that we could also choose more 
sophisticated loss functions based on \cite{ZAFFALON20121282}.
%%% MT to TB: I added "we sum these losses together across all preds"; check
We sum these losses together across all predictors
to obtain the total loss, presented in \cref{tab:misspec}.
The table counts the number of
false positives (FP) and false negatives (FN). For RBCE, we have an
additional column (ID)
which counts the number of indeterminate predictors.
From the table it can be seen that for the first scenario, our method
abstains from identifying some variables for 
$n <50$. Especially for $n=25$, our method identifies 26 and 23 variables as indeterminate
for the first setting and second setting respectively. However,
later on our method gives more precise results in terms of variable
selection. We also notice that BSSL tends to perform poorly
in terms of variable selection for $n=25$. This can be seen
from the causal effect estimation as well.
Moreover, we observe that for the second setting both SSCE
and BSSCE underperform in identifying the active variables, which can 
be explained from \cref{tab:causal} as well.
